Pillar 1 - Sequential Pattern Mining

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
minor changes

# Setup
load previous data and create function to find courses
```{r loading data}
load("data_pillar_1.RDATA")
```

@@

}
```

#Simple Rule Mining
##Data Exploration of Transcripts
```{r}
exploration <- d_transcript %>%
  mutate(Grade = case_when(Grade == "NG"~ "-1", #"0,0", #maybe we could just remove these from the analysis and treat them separately?
                           T~Grade),
         Grade = str_replace(string = Grade, pattern = ",",replace = "."),
         Grade = as.numeric(Grade))%>%
  filter(!is.na(Grade)) %>%
  filter(Grade != -1) #remove NG

summary(exploration)

student_statistics <- exploration %>%
  group_by(`Student ID`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = mean(Grade), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

course_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  filter(between(Year_numerical, 2015,2016)) %>% #filter year
  group_by(`Course ID`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5)) %>%
  inner_join(select(d_course,`Course ID`, `Course Title`), by = "Course ID")

concentration_statistics <- exploration %>%
  inner_join(select(d_course,-Period, -`Period (additional)`,-`Period (additional bis)`,-`Course Title`), by = "Course ID") %>%
  #left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
  group_by(Concentration) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

cluster_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Cluster) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

year_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Year_numerical) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

level_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Level) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

percentage_grades_awarded <- d_transcript %>%
          mutate(Grade = str_replace(string = Grade, pattern = ",",replace = "."),
                 Grade = as.integer(Grade)) %>%
  filter(Year_numerical %in% c(2015,2016))%>%
  mutate(total=n())%>%
  group_by(Grade) %>%
  mutate(grade_total=n())%>%
  select(Grade, grade_total,total)%>%
  distinct()%>%
  mutate(Percentage = signif(grade_total/total,digits=2))%>%
  arrange(Grade)

```
We have found some NA values for the grades! Students:

0177849 - COR1003 & EMTH0001  +++++++++++++++ Master thesis should not be showing up! +++++++++++++
0177857
0222100
0270148
0313173
0317101
0317349

```{r}
#We have NA in grades. Something weird is happening. 
summary(str_detect(d_transcript$Grade, pattern="NA")) #shows NA's = 312 FALSE= 89069 WHY ARE THERE NAs?

has_na <- d_transcript %>%
  mutate(What = str_detect(Grade, pattern="NA")) %>%
  filter(is.na(What))
```

>>>>

# Setup
load previous data and create function to find courses
```{r loading data}
load("Output/data_pillar_1.RDATA")
```

@@

}

# Example
find_course("HUM1005")
```

#Simple Rule Mining
##Data Exploration of Transcripts
```{r}

# For convenience
provide_statistics <- function(data){
  data %>%
    summarise(
      n      = n(),
      Min    = min(Grade),
      Max    = max(Grade), 
      Mean   = round(mean(Grade), 2), 
      Median = median(Grade), 
      SD        = round(sd(Grade), 2),
      Fail_rate = round(mean(Fail), 2),
      Fail_n = sum(Fail)
      )
}

# Student level
d_transcript %>%
  group_by(`Student ID`) %>%
  provide_statistics()

# Course level
d_transcript %>%
  inner_join(d_course, by = c("Course ID")) %>%
  group_by(`Course ID`) %>%
  provide_statistics()

# Cluster level
d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  filter(!is.na(Cluster)) %>%
  group_by(Cluster) %>%
  provide_statistics()

# Concentration evel
d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
  group_by(Concentration) %>%
  provide_statistics()

# Year level
d_transcript %>%
  group_by(Year_numerical) %>%
  provide_statistics()

# Level level
d_transcript %>%
  inner_join(d_course, by = c("Course ID")) %>%
  filter(!is.na(Level)) %>%
  group_by(Level) %>%
  provide_statistics()
```
